Demo arXiv template

### 2022-10-18 paper/paper.qmd
more tweak

Currently, index construction lacks structure. 
It is often up to the researchers to decide whether to provide open source code on the new indices, what would be the best user interface for the new indices, and how easily the new indices can be used by end users, along with other existing indices. 
This causes the problem that indices are often designed separately and many indices simply lump all the steps into a [single command function]. 
While this simplifies the amount of code needed to derive index values from a set of inputs, many problems arise when the code is adopted outside the research group that wrote the index. 
First of all, indices created by a single command provide little room for modification.
For example, many indices involve a step to fit variables into a particular distribution.
Index researchers may provide options for different fits, but it is generally hard to experiment with options outside the provided distributions.
Also, many indices share similar or identical steps in part of their construction, a [single command function] eliminates the possibility to borrow codes written by others and forces researchers to rebuild the wheels when creating new indices.
Lastly, users may wish to inspect intermediate results during the index construction to validate the output or to compare results with other indices, but [single command functions] do not support this demand unless the users can customise the source code as they need.

@@

Ideally each command corresponds to a user action

While jumbled indices jumble in their own ways, perspicuous indices are all alike. 
A clear pipeline for indices construction brings transparency to the algorithm. 
Many often, official websites like National Oceanic and Atmospheric Administration (NOAA) will regularly updates the raw data and the indices calculated for users' consumption and provides description of the methodology. 
However, the source code and the scripts is usually not publicly available and there is no tool, or users need to be its own tool, to verify the calculation. 
Once a data pipeline is built, users can follow the steps in the index construction to validate the numbers published by the authorities. 
Once a data pipeline is constructed, it opens possibility to do statistics on indices.
For example, bootstrap and other methods could be applied into the pipeline to calculate uncertainty on the index value with randomisation. 
Properties of existing indices can be examined through swapping the steps involved in the construction. 
For example, some indices prefer to standardise the input variables in the beginning of the workflow while other prefer to move the standardisation towards the end and directly apply it on the index value. 
A flexible pipline approach gives the freedom to construct the index in both ways by placing the standardisation step in different stages of the pipeline. 
The importance of the position of a single steps can be compared through indices constructed by placing the step at different stages of the pipeline. 
Also, the pipeline approach motivates new indices through combining existing steps from different indices.

<!-- - transparency: official published, can decompose the indices,  -->
<!-- - allow for calculation on uncertainty with randomization,  -->
<!-- - compare indices, -->
<!-- - tweak/ swap building blocks,  -->
<!-- - create new indices based on combinations of existing steps. -->

>>>>

Currently, index construction lacks structure. 
It is often up to the researchers or research institutions to decide whether to provide open source code on the new indices, what would be the best user interface for the new indices, and how easily the new indices can be used by end users, along with other existing indices. 
Institutes like National Oceanic and Atmospheric Administration (NOAA) and United States Drought Monitor (USDM) moderate the indices in their domains.
They provide public information to describe the methodology used in the calculation, publish the index values for public consumption while the source code used for computing is often not available for public consumption. 
For researchers, the level of varies. Some research groups provide open sourced code available for [explain situation with individual researchers]
This causes the problem that computation on indices are not transparent and code design on indices are done separately.
Researchers who wish to validate the calculation from large institutes need to reinvent the wheels that have already been built.
Open source codes provide narrow margin for adjustment. [more here]
<!-- For example, many indices involve a step to fit variables into a particular distribution. -->
<!-- Index researchers may provide options for different fits, but it is generally hard to experiment with options outside the provided distributions. -->
Similar steps used by different indices are difficult to spot since they all hide under commands for calculating different indices. 
Lastly, these functions does not support inspecting intermediate results if users wish to check the output of a certain step.

<!-- users may wish to inspect intermediate results during the index construction to validate the output or to compare results with other indices, but [single command functions] do not support this demand unless the users can customise the source code as they need. -->

@@

*This week: need to extend each point of why it is beneficial further with more information?*

While jumbled indices jumble in their own ways, perspicuous indices are all alike. 
This paper proposes a data pipeline for index construction. [more on what we bring onto the table: construct indices through pipeline steps where each step corresponds to a single building block???]

The pipeline framework provides an open source tool to construct indices in general. This is beneficial because it opens up the possibility to create, study, and use indices in a more principled way. 
More specifically, it enables researchers to 1) validate the indices calculated from external organisations, 2) unify various indices under the same framework for comparison, 3) swap or adjust individual steps in the index construction to study their contribution, 4) calculate uncertainty  on indices, and finally, 5) inspire proposal of new indices from existing ones.

<!-- Once a data pipeline is constructed, it opens possibility to do statistics on indices. -->
<!-- For example, bootstrap and other methods could be applied into the pipeline to calculate uncertainty on the index value with randomisation.  -->
<!-- Properties of existing indices can be examined through swapping the steps involved in the construction.  -->
<!-- For example, some indices prefer to standardise the input variables in the beginning of the workflow while other prefer to move the standardisation towards the end and directly apply it on the index value.  -->
<!-- A flexible pipline approach gives the freedom to construct the index in both ways by placing the standardisation step in different stages of the pipeline.  -->
<!-- The importance of the position of a single steps can be compared through indices constructed by placing the step at different stages of the pipeline.  -->
<!-- Also, the pipeline approach motivates new indices through combining existing steps from different indices.  -->

### 2022-10-18 paper/paper.tex
more tweak

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, borderline west={3pt}{0pt}{shadecolor}, interior hidden, enhanced, boxrule=0pt, breakable, frame hidden]}{\end{tcolorbox}}\fi

@@

\emph{indices constructed separately, but there are lots of are same
{[}!{]}, but hard to see from the current construction. ``messy data are
messy in there own way''. Describe how they are same, so we can modular
them}

There has not yet been a standardised workflow on index construction.
For simple indices, users may be able to work out the calculation from
the equations or workflow provided, while for more complicated
construction, software is not even available for open-source
consumption. Even when the software implementation is available, most
indices are computed through a single index command, {[}given examples
but not too domain specific{]}. This software design focuses on the name
of the index and includes all the steps in a single index function. With
this design, there is little room for modification. For example, fit a
new distribution that is not provided in the initial code. Also, when
scaled to a large number of indices, it increases the cognitive load of
remembering hundreds of index names. A better approach is to modularise
these steps and construct a pipeline for users to build indices through
choosing different building blocks from each module. With this design,
users focus on the operations involved in the index construction. If an
operation from another index is useful, users can borrow it to modify an
existing index.

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners, enhanced, interior hidden, boxrule=0pt, breakable]}{\end{tcolorbox}}\fi

@@

\emph{From last week: indices constructed separately, but there are lots
of are same {[}!{]}, but hard to see from the current construction.
``messy data are messy in there own way''. Describe how they are same,
so we can modular them}

Currently, index construction lacks structure. It is often up to the
researchers or research institutions to decide whether to provide open
source code on the new indices, what would be the best user interface
for the new indices, and how easily the new indices can be used by end
users, along with other existing indices. Institutes like National
Oceanic and Atmospheric Administration (NOAA) and United States Drought
Monitor (USDM) moderate the indices in their domains. They provide
public information to describe the methodology used in the calculation,
publish the index values for public consumption while the source code
used for computing is often not available for public consumption. For
researchers, the level of varies. Some research groups provide open
sourced code available for {[}explain situation with individual
researchers{]} This causes the problem that computation on indices are
not transparent and code design on indices are done separately.
Researchers who wish to validate the calculation from large institutes
need to reinvent the wheels that have already been built. Open source
codes provide narrow margin for adjustment. {[}more here{]} Similar
steps used by different indices are difficult to spot since they all
hide under commands for calculating different indices. Lastly, these
functions does not support inspecting intermediate results if users wish
to check the output of a certain step.

\emph{This week: need to extend each point of why it is beneficial
further with more information?}

While jumbled indices jumble in their own ways, perspicuous indices are
all alike. This paper proposes a data pipeline for index construction.
{[}more on what we bring onto the table: construct indices through
pipeline steps where each step corresponds to a single building
block???{]}

The pipeline framework provides an open source tool to construct indices
in general. This is beneficial because it opens up the possibility to
create, study, and use indices in a more principled way. More
specifically, it enables researchers to 1) validate the indices
calculated from external organisations, 2) unify various indices under
the same framework for comparison, 3) swap or adjust individual steps in
the index construction to study their contribution, 4) calculate
uncertainty on indices, and finally, 5) inspire proposal of new indices
from existing ones.
